%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{bibentry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Anders Aamand} % Your name
%\address{Sankt Hans Gades Passage 7, 4th, 2200, Copenhagen, Denmark} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{aamand@mit.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Current Employment}
{\bf University of Copenhagen, BARC} \hfill {\em March 2024 - Present} 
\\ Postdoctoral Researcher at BARC


\end{rSection}

\begin{rSection}{Past Employment}
{\bf MIT, Electrical Engineering and Computer Science} \hfill {\em August 2021 - January 2024} 
\\ Postdoctoral Researcher in Piotr Indyk's group \\ \\
{\bf University of Copenhagen, BARC} \hfill {\em September 2020 - July 2021} 
\\ Postdoctoral Researcher at BARC


\end{rSection}



\begin{rSection}{Education}

{\bf University of Copenhagen, BARC} \hfill {\em September 2017 - August 2020} 
\\ PhD student within algorithms. \\Supervisor: Mikkel Thorup
\\ Phd degree awarded in October 2020\\
\\{\bf University of Copenhagen} \hfill {\em September 2016 - August 2017}  
\\ Master of Mathematics 
\\ GPA: 12. \\
\\{\bf University of Cambridge, Clare Hall} \hfill {\em October 2015 - June 2016} 
\\ Master of Advanced Study (Part III of the Mathematical Tripos)
\\ Supervisor: Imre Leader. 
\\ Final exam result: Pass with Distinction \\
\\{\bf University of Copenhagen} \hfill {\em September 2012 - June 2015} 
\\ Bachelor of Mathematics
\\ GPA: 11.75 
\end{rSection}

\begin{rSection}{Publications}
\bibliographystyle{unsrt}
\nobibliography{ref}
\begin{enumerate}
	\item \bibentry{2023Improvedfreqest}
	\item \bibentry{2023IPclustering}
	\item \bibentry{2023Density}
	\item \bibentry{2023Tiling}
	\item \bibentry{2023Decremental}
	\item \bibentry{2023Sorting}
	\item \bibentry{2023Experts}
	\item \bibentry{2022NoRepetition}
	\item \bibentry{2022Monotone}
	\item \bibentry{2022Matching}
	\item \bibentry{2022Weisfeiler}
	\item \bibentry{DBLP:conf/stoc/AamandKT21}
	\item \bibentry{contactgraphs}
	\item \bibentry{tabperm}
	\item \bibentry{nonemptybins}
	\item \bibentry{dchoices}
	\item \bibentry{trailorientations}
	\item \bibentry{diskinbcccurve}\end{enumerate}
\end{rSection}



\begin{rSection}{Teaching experience}
 \begin{itemize}
 \item Lecturer at seminar on spectral expansion (UCPH, DIKU) \hfill{\emph{2019}}
 \item Lecturer at seminar on similarity search (UCPH, DIKU) \hfill{\emph{2018}}
 \item Lecturer in \emph{Topics in Algorithms and Data Structures} (UCPH, DIKU) \hfill{\emph{2018}}
 \item Teaching assistant in \emph{Advanced Algorithms and Data Structures} (UCPH, DIKU) \hfill{\emph{2018}}
 \item Teaching assistant at various courses within discrete mathematics, probability and \\ statistics, geometry, analysis, and linear algebra (UCPH, MATH) \hfill{\emph{2012-2017}}
 \item Mathematics teacher at Danish High School \emph{Ingrid Jespersens Gymnasieskole} \hfill{\emph{2013-2014}}
 \end{itemize}
 \end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards and achievements}
\begin{itemize}
\item International Postdoc Grant from the Independent Research Fund Denmark  \hfill{\emph{2020}} 
\item Elite Research Travel Grant, Ministry of Higher Education and Science  \hfill{\emph{2019}} 
\item Participated in the International Mathematical Olympiad as part of the Danish \\ national team  \hfill{\emph{2011}}
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Scientific stays abroad}
\begin{itemize}
\item Visiting student at Massachusetts Institute of Technology, CSAIL. \\Supervisor: Piotr Indyk. \hfill{\emph{March 2019 - May 2019}}
\item Visiting student at Columbia University, DSI. \\ Supervisor: Alexandr Andoni. \hfill{\emph{June 2019 - September 2019}}
\item Visiting student at the University of Cambridge.  \\Supervisor: Imre Leader. \hfill{\emph{December 2019}}
\end{itemize}

\end{rSection}


\begin{rSection}{Other professional activities}
\begin{itemize}
\item Programme committee member at SWAT'24
\item Referee for conferences and journals: NeurIPS, ICML, JACM, STOC, SODA, ICALP, SoCG, CPM.
\end{itemize}

\end{rSection}


\begin{rSection}{Language skills}
\item Danish: Native
\item English: Fluent
\item French: Intermediate
\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\end{document}